Supplementary Figures relative to the SVA-DEA benchmark

### 2020-08-04 supplementary_figures/imputation.Rmd
updated supplementary figures, changing figure labels

# Supplementary Figure `r getFigNb(TRUE)`

@@

### Supplementary Figure `r getFigNb()`
**Evaluation of imputation/denoising methods.** Average silhouette width (**A**) and clustering accuracy (**B**) with or without (indicated as _none_) application of a denoising/imputation method.

>>>>

# Fig S`r getFigNb(TRUE)`

@@

### Fig S`r getFigNb()`
**Evaluation of imputation/denoising methods.** Average silhouette width (**A**) and clustering accuracy (**B**) with or without (indicated as _none_) application of a denoising/imputation method.

### 2020-08-04 supplementary_figures/supp1_dataset_description.Rmd
updated supplementary figures, changing figure labels

### Supplementary Figure `r getFigNb()`
The total counts and total features per cell of doublets (red) versus other cells. We used the demuxlet annotation of doublets (based on SNPs) made available through CellBench. The lines indicate, respectively, 2, 2.5, and 3 median absolute deviations. While doublets tend to have a higher total count and especially number of detected features, these features alone are not always sufficient for their identification.

@@

### Supplementary Figure `r getFigNb()`
Distribution across cells of various control properties in the different datasets. The 
lines indicate respectively 2 and 5 median absolute deviations (MADs).

@@

### Supplementary Figure `r getFigNb()`
Relationship between selected cell-level QC metrics.

@@

### Supplementary Figure `r getFigNb()`
There is a tight relationship, in 10x datasets (i.e. not the `Koh` and `Kumar` datasets), between the total counts of a cell and its number of detected features. We therefore include, among control variables, deviation from this ratio.

@@

### Supplementary Figure `r getFigNb()`
Relationship between various cellular properties and the frequency of cluster mis-assignment for the mixology10x3cl (A) and mixology10x5cl (B) datasets. The percentage of misclassification refers to the frequency with which a given cell is assigned the wrong cluster (using the Hungarian algorithm for cluster matching) across several hundred clustering runs with varying parameters. Since some subpopulations tend to be more misclassified than others, the adjusted rate of misclassification (`adj_mis`) is substracted for the subpopulation median misclassification rate.

@@

### Supplementary Figure `r getFigNb()`
Relationship between various cellular properties and the frequency of cluster mis-assignment for the Zheng equal (A) or unequal (B) mixtures of four cell types. See Supplementary Figure `r getFigNb()-1` for more information. The only clear pattern is that cells with a high number of reads or features tend to have a higher misclassification rate.

@@

### Supplementary Figure `r getFigNb()`
Relationship between various cellular properties and the frequency of cluster mis-assignment for the Zheng mixture of 8 cell types. See Supplementary Figure `r getFigNb()-2` for more information.

>>>>

### Fig S`r getFigNb()`
The total counts and total features per cell of doublets (red) versus other cells. We used the demuxlet annotation of doublets (based on SNPs) made available through CellBench. The lines indicate, respectively, 2, 2.5, and 3 median absolute deviations. While doublets tend to have a higher total count and especially number of detected features, these features alone are not always sufficient for their identification.

@@

### Fig S`r getFigNb()`
Distribution across cells of various control properties in the different datasets. The 
lines indicate respectively 2 and 5 median absolute deviations (MADs).

@@

### Fig S`r getFigNb()`
Relationship between selected cell-level QC metrics.

@@

### Fig S`r getFigNb()`
There is a tight relationship, in 10x datasets (i.e. not the `Koh` and `Kumar` datasets), between the total counts of a cell and its number of detected features. We therefore include, among control variables, deviation from this ratio.

@@

### Fig S`r getFigNb()`
Relationship between various cellular properties and the frequency of cluster mis-assignment for the mixology10x3cl (A) and mixology10x5cl (B) datasets. The percentage of misclassification refers to the frequency with which a given cell is assigned the wrong cluster (using the Hungarian algorithm for cluster matching) across several hundred clustering runs with varying parameters. Since some subpopulations tend to be more misclassified than others, the adjusted rate of misclassification (`adj_mis`) is substracted for the subpopulation median misclassification rate.

@@

### Fig S`r getFigNb()`
Relationship between various cellular properties and the frequency of cluster mis-assignment for the Zheng equal (A) or unequal (B) mixtures of four cell types. See Supplementary Figure `r getFigNb()-1` for more information. The only clear pattern is that cells with a high number of reads or features tend to have a higher misclassification rate.

@@

### Fig S`r getFigNb()`
Relationship between various cellular properties and the frequency of cluster mis-assignment for the Zheng mixture of 8 cell types. See Supplementary Figure `r getFigNb()-2` for more information.

### 2020-08-04 supplementary_figures/supp1b_metrics.Rmd
updated supplementary figures, changing figure labels

### Supplementary Figure `r getFigNb()`
The number of clusters called has a much bigger impact on the Adjusted Rand Index (ARI) than differences between methods. The dashed line indicates the true number of clusters.

# Supplementary Figure `r getFigNb(TRUE)`

@@

### Supplementary Figure `r getFigNb()`
Relationship of various metrics of clustering accuracy between each other and with variations in the number of clusters called (`nbClust.diff` and `nbClust.absDiff`). Correlations were calculated for each dataset separately across various clustering runs and averaged (the `mixology10x3cl` dataset was excluded due to insufficient variation among the results). Information distance metrics (ID, NID, VI, NVI) are highly correlated with the absolute difference between the true and called number of clusters, while the Adjusted Rand Index (ARI) and similar metrics were strongly anticorrelated to it. Precision (mean_pr) and recall (mean_re) were slightly less correlated with discrepancies in the number of clusters. Mutual information (MI) was not at all correlated with the absolute difference in number of clusters (`nbClust.absDiff`), but positively correlated with the difference (`nbClust.diff`), i.e. favouring clusterings calling a higher number of clusters. We therefore recommend using complementary metrics such as ARI and MI, and potentially mean F1 per subpopulation.

>>>>

### Fig S`r getFigNb()`
The number of clusters called has a much bigger impact on the Adjusted Rand Index (ARI) than differences between methods. The dashed line indicates the true number of clusters.

# Fig S`r getFigNb(TRUE)`

@@

### Fig S`r getFigNb()`
Relationship of various metrics of clustering accuracy between each other and with variations in the number of clusters called (`nbClust.diff` and `nbClust.absDiff`). Correlations were calculated for each dataset separately across various clustering runs and averaged (the `mixology10x3cl` dataset was excluded due to insufficient variation among the results). Information distance metrics (ID, NID, VI, NVI) are highly correlated with the absolute difference between the true and called number of clusters, while the Adjusted Rand Index (ARI) and similar metrics were strongly anticorrelated to it. Precision (mean_pr) and recall (mean_re) were slightly less correlated with discrepancies in the number of clusters. Mutual information (MI) was not at all correlated with the absolute difference in number of clusters (`nbClust.absDiff`), but positively correlated with the difference (`nbClust.diff`), i.e. favouring clusterings calling a higher number of clusters. We therefore recommend using complementary metrics such as ARI and MI, and potentially mean F1 per subpopulation.

### 2020-08-04 supplementary_figures/supp2_filtering.Rmd
updated supplementary figures, changing figure labels

### Supplementary Figure `r getFigNb()`
Mean clustering F1 score per subpopulation, mean F1 at true number of clusters, as well as maximum and median proportion of excluded cells per subpopulation across various filtering strategies. Doublet removal generally improves clustering accuracy with relatively mild increases exclusion rates, even in datasets that do not have heterotypic doublets. Stringent distribution-based filtering creates large cell type biases.

@@

### Supplementary Figure `r getFigNb()`

>>>>

### Fig S`r getFigNb()`
Mean clustering F1 score per subpopulation, mean F1 at true number of clusters, as well as maximum and median proportion of excluded cells per subpopulation across various filtering strategies. Doublet removal generally improves clustering accuracy with relatively mild increases exclusion rates, even in datasets that do not have heterotypic doublets. Stringent distribution-based filtering creates large cell type biases.

@@

### Fig S`r getFigNb()`

### 2020-08-04 supplementary_figures/supp3_normalization.Rmd
updated supplementary figures, changing figure labels

### Supplementary Figure `r getFigNb()`
Mean per-subpopulation absolute correlation of the first 5 components with library size (left) and the number of detected features (right) across normalization procedures.

@@

### Supplementary Figure `r getFigNb()`
Mean difference between the number of detected clusters and the number of real subpopulations, depending on the normalization method, the resolution and the number of dimensions used. The Kumar dataset is not shown here due to a lack of variation in the number of clusters detected. A rough ANOVA on `nbClusters~dataset+norm+dims+resolution` suggests that seuratvst (sctransform) is associated with a higher number of clusters (p~`r round(mod$coefficients["normnorm.sctransform",4],3)`).

@@

### Supplementary Figure `r getFigNb()`
Relationship of the variance with mean count after `sctranform`'s variance stabilizing transformation.

@@

### Supplementary Figure `r getFigNb()`
Running time of the normalization methods.

>>>>

### Fig S`r getFigNb()`
Mean per-subpopulation absolute correlation of the first 5 components with library size (left) and the number of detected features (right) across normalization procedures.

@@

### Fig S`r getFigNb()`
Mean difference between the number of detected clusters and the number of real subpopulations, depending on the normalization method, the resolution and the number of dimensions used. The Kumar dataset is not shown here due to a lack of variation in the number of clusters detected. A rough ANOVA on `nbClusters~dataset+norm+dims+resolution` suggests that seuratvst (sctransform) is associated with a higher number of clusters (p~`r round(mod$coefficients["normnorm.sctransform",4],3)`).

@@

### Fig S`r getFigNb()`
Relationship of the variance with mean count after `sctranform`'s variance stabilizing transformation.

@@

### Fig S`r getFigNb()`
Running time of the normalization methods.

### 2020-08-04 supplementary_figures/supp4_selection.Rmd
updated supplementary figures, changing figure labels

### Supplementary Figure `r getFigNb()`
**A:** Comparison of the gene-wise proportion of variance explained by real subpopulations based on Seurat's standard log normalization and on `sctransform` variance-stabilizing transformation. Across 10x datasets, there is a good agreement between the two, the correlation ranging between 0.92 and 0.97.
**B:** There is also a good agreement between _variance_ and _deviance_ explained, with some genes having a higher deviance explained.
**C-D:** Relationship between mean expression and the difference between the proportion of deviance explained and the proportion of variance explained in two datasets. Genes that have a higher proportion of the deviance explained than of the variance explained are generally the lowly-expressed ones.

>>>>

### Fig S`r getFigNb()`
**A:** Comparison of the gene-wise proportion of variance explained by real subpopulations based on Seurat's standard log normalization and on `sctransform` variance-stabilizing transformation. Across 10x datasets, there is a good agreement between the two, the correlation ranging between 0.92 and 0.97.
**B:** There is also a good agreement between _variance_ and _deviance_ explained, with some genes having a higher deviance explained.
**C-D:** Relationship between mean expression and the difference between the proportion of deviance explained and the proportion of variance explained in two datasets. Genes that have a higher proportion of the deviance explained than of the variance explained are generally the lowly-expressed ones.

### 2020-08-04 supplementary_figures/supp5_dr.Rmd
updated supplementary figures, changing figure labels

### Supplementary Figure `r getFigNb()`
**Evaluation of common dimensionality reduction methods. A:** Minimum (left) and average (right) silhouette width per subpopulation resulting from combinations of normalization and dimension reductions. **B:** Clustering accuracy, measured by mutual information (MI), minimum subpopulation precision, and adjusted Rand index (ARI) at the true number of clusters.

@@

### Supplementary Figure `r getFigNb()`
Mean difference between the number of detected clusters and the number of real subpopulations, depending on the resolution and number of dimensions used. Based on sctransform and seurat PCA. Increasing the number of dimensions tends to decrease the number of identified clusters, especially at resolutions around the default value.

@@

### Supplementary Figure `r getFigNb()`
Estimates of dimensionality by the `intrinsicDimension::maxLikGlobalDimEst` method using various 'reasonable' numbers of nearest neighbors (`k` parameter).

>>>>

### Fig S`r getFigNb()`
**Evaluation of common dimensionality reduction methods. A:** Minimum (left) and average (right) silhouette width per subpopulation resulting from combinations of normalization and dimension reductions. **B:** Clustering accuracy, measured by mutual information (MI), minimum subpopulation precision, and adjusted Rand index (ARI) at the true number of clusters.

@@

### Fig S`r getFigNb()`
Mean difference between the number of detected clusters and the number of real subpopulations, depending on the resolution and number of dimensions used. Based on sctransform and seurat PCA. Increasing the number of dimensions tends to decrease the number of identified clusters, especially at resolutions around the default value.

@@

### Fig S`r getFigNb()`
Estimates of dimensionality by the `intrinsicDimension::maxLikGlobalDimEst` method using various 'reasonable' numbers of nearest neighbors (`k` parameter).

### 2020-08-04 supplementary_figures/supp6_clust.Rmd
updated supplementary figures, changing figure labels

### Supplementary Figure `r getFigNb()`
Difference between the number of detected clusters and the number of real subpopulations according to different clustering paramters.

>>>>

### Fig S`r getFigNb()`
Difference between the number of detected clusters and the number of real subpopulations according to different clustering paramters.

### 2020-08-04 supplementary_figures/supp_figures.Rmd
added missing supp figures
some figure updates
updated supplementary figures, changing figure labels

---
title: \vspace{2cm}\Large{pipeComp, a general framework for the evaluation of computational pipelines, reveals performant single-cell RNA-seq preprocessing tools}
subtitle: \vspace{2cm}\LARGE{Supplementary Figures}\vspace{2cm}
date: "`r format(Sys.time(), '%d %B, %Y')`"
author:
- "Pierre-Luc Germain"
- "Anthony Sonrel"
- "Mark D. Robinson"
geometry: margin=1.5cm
output:
  pdf_document:
    fig_width: 8
    fig_height: 6
    citation_package: natbib
bibliography: ../bmc_article.bib
---

\renewcommand{\thepage}{S\arabic{page}}

@@

### Supplementary Figure `r getFigNb()`: Overview of the benchmark datasets

@@

```{r child='supp1b_metrics.Rmd'}
```

```{r child='supp1_dataset_description.Rmd'}
```

```{r child='supp2_filtering.Rmd'}
```

```{r child='supp3_normalization.Rmd'}
```

```{r child='supp4_selection.Rmd'}
```

```{r child='supp5_dr.Rmd'}
```

@@

@@

### Supplementary Figure `r getFigNb()`: Summary of the recommendations.

>>>>

---
title: \vspace{2cm}\Large{pipeComp, a general framework for the evaluation of computational pipelines, reveals performant single-cell RNA-seq preprocessing tools}
subtitle: \vspace{2cm}\LARGE{Additional File 1 - Supplementary Figures}\vspace{2cm}
date: "`r format(Sys.time(), '%d %B, %Y')`"
author:
- "Pierre-Luc Germain"
- "Anthony Sonrel"
- "Mark D. Robinson"
geometry: margin=1.5cm
output:
  pdf_document:
    fig_width: 8
    fig_height: 6
    citation_package: natbib
bibliography: ../bmc_article.bib
---

@@

### Fig S`r getFigNb()`: Overview of the benchmark datasets

@@

```{r child='supp1b_metrics.Rmd', cache=TRUE}
```

```{r child='supp1_dataset_description.Rmd', cache=TRUE}
```

```{r child='supp2_filtering.Rmd', cache=TRUE}
```

```{r child='supp3_normalization.Rmd', cache=TRUE}
```

```{r child='supp4_selection.Rmd', cache=TRUE}
```

```{r child='supp5_dr.Rmd', cache=TRUE}
```

@@

```{r child='supp_overall.Rmd'}
```

```{r child='imputation.Rmd'}
```

@@

### Fig S`r getFigNb()`: Summary of the recommendations.

### 2020-08-04 supplementary_figures/supp_framework/supp_framework_explanations.Rmd
updated supplementary figures, changing figure labels

---
title: "pipeComp - Supplementary Methods"
author: Pierre-Luc Germain, Anthony Sonrel, Mark D. Robinson
output:
  pdf_document:
    toc: true
    number_sections: true
    toc_depth: 2
urlcolor: blue
---

@@

On the other hand, a `r CRANpkg("drake")`-based workflow has several advantages, in particular the capacity, upon failure of a pipeline (or changes made to a step), to recover and restart from the very next upstream target. We are currently working on an `bptry`-based approach to error handling and selective recomputation, but for the moment users requiring smooth error recovery should rather rely on `r CRANpkg("drake")`.

>>>>

---
title: "pipeComp - Additional file 2: Supplementary Methods"
author: Pierre-Luc Germain, Anthony Sonrel, Mark D. Robinson
output:
  pdf_document:
    toc: true
    number_sections: true
    toc_depth: 2
urlcolor: blue
---

@@

On the other hand, a `r CRANpkg("drake")`-based workflow has several advantages, in particular the capacity, upon failure of a pipeline (or changes made to a step), to smoothly recover and restart from the very next upstream target. Starting from version 0.99.45, `r Rpackage("pipeComp")` also supports some error handling, allowing users to use results from those pipelines that ran successfully and selectively recompute (e.g. after fixing the error) those that encountered errors (see the package's vignettes for more information). However, due to the non-persistent nature of `r Rpackage("pipeComp")`'s storage, for those parameter combinations that failed, all steps will have to be recomputed.

### 2020-08-04 supplementary_figures/supp_overall.Rmd
updated supplementary figures, changing figure labels

---
title: "Supplementary Figures relative to feature selection"
author: "Pierre-Luc Germain"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

@@

suppressPackageStartupMessages({
  library(ggplot2)
  library(cowplot)
  library(ComplexHeatmap)
  library(pipeComp)
})
theme_set(theme_cowplot(font_size = 11))
source("../misc_functions.R")
```

# Supplementary Figure `r getFigNb(TRUE)`

```{r, fig.width=6, fig.height=5}
ov <- readRDS("../data/overall.rds")

cl <- ov$evaluation$clustering
cl$norm <- relevel(cl$norm, "norm.seurat")
cl$doubletmethod <- relevel(cl$doubletmethod, "none")
cl$filt <- relevel(cl$filt, "none")
cl$sel <- relevel(cl$sel, "sel.vst")
cl$clustmethod <- relevel(cl$clustmethod, "clust.seurat")
cl$clustmethod <- relevel(cl$clustmethod, "clust.seurat")

ff <- function(x, trueK=FALSE){
  f <- paste0(x,"~dataset+resolution*dataset+doubletmethod+sel+filt+norm+clustmethod+dims")
  if(trueK) cl <- cl[cl$n_clus==cl$true.nbClusts,]
  mod <- lm(as.formula(f), data=cl)
  co <- as.data.frame(coef(summary(mod)))
  co <- co[grep("sctransfrom|scran|filt|elbow|doublet|Annoy", row.names(co)),]
  colnames(co)[2:4] <- c("stderr","t","pvalue")
  co$coef <- gsub(" +$","",row.names(co))
  aov <- as.data.frame(summary(aov(mod))[[1]])[,-1]
  aov <- aov[grep("^Residuals|resolution|dataset", row.names(aov), invert=TRUE),]
  aov$varExpl <- aov[,1]/sum(aov[,1])
  aov <- aov[grep("^Residuals", row.names(aov), invert=TRUE),4:5]
  colnames(aov)[1] <- "pvalue"
  aov$parameter <- gsub(" +$","",row.names(aov))
  list( coefs=co, aov=aov )
}

cos <- lapply(c(MI="MI",ARI="ARI",minPre="min_pr"), FUN=ff)
aov <- dplyr::bind_rows(lapply(cos, FUN=function(x) x$aov), .id="metric")

cos2 <- lapply(c(ARI="ARI"), trueK=TRUE, FUN=ff)
aov2 <- dplyr::bind_rows(lapply(cos2, FUN=function(x) x$aov), .id="metric")
p1 <- ggplot(aov, aes(reorder(parameter, -varExpl), varExpl, group=parameter, fill=metric)) + 
  geom_col() + xlab("") + ylab("Proportion of variance explained") + coord_flip()
p2 <- ggplot(aov2, aes(reorder(parameter, -varExpl), varExpl, group=parameter, fill=metric)) + 
  geom_col() + xlab("") + ylab("Variance explained") + theme(legend.position="none") + 
  coord_flip() + ggtitle("ARI at true k")

co <- dplyr::bind_rows(lapply(cos, FUN=function(x) x$coef), .id="metric")
co2 <- dplyr::bind_rows(lapply(cos2, FUN=function(x) x$coef), .id="metric")
for(f in c("norm","filt","doubletmethod","dims","sel","clustmethod")){
  co$coef <- gsub(paste0("^",f),"",co$coef)
  co2$coef <- gsub(paste0("^",f),"",co2$coef)
}
p3 <- ggplot(co, aes(coef, Estimate, group=coef, fill=metric)) + geom_col() + xlab("") +
  ylab("Estimated coefficient") + geom_hline(yintercept = 0, linetype="dashed") + 
  coord_flip() + theme(legend.position="none")
p4 <- ggplot(co2, aes(coef, Estimate, group=coef, fill=metric)) + geom_col() + xlab("") +
  ylab("Estimated coefficient") + geom_hline(yintercept = 0, linetype="dashed") + 
  coord_flip() + theme(legend.position="none")

# plot_grid( plot_grid(p1,p2,rel_widths=c(4,3),labels=LETTERS[1:2]),
#            plot_grid(p3,p4,rel_widths=c(4,3),labels=LETTERS[3:4]),
#            nrow=2, rel_heights=c(3,4))
plot_grid(p1 + ylab("Proportion of variance in metric explained by the parameter"),p2,nrow=2,labels=LETTERS[1:2])
```

### Supplementary Figure `r getFigNb()`

**A:** Proportion of the variance in clustering accuracy metrics explained by main parameters. **B:** Proportion of the variance in Adjusted Rand Index (ARI) explained by the parameters, among the analyses giving the true number of clusters. The ANOVA were performed with the model

`metric ~ dataset*resolution+doubletmethod+filt+sel+norm+clustmethod+dims`

In both panels, the proportion is calculated after substracting the variance attributable to differences due to the dataset, the resolution and their interaction. The alternatives included in the analysis (other than the default ones described in the methods) were: 
```
list( doubletmethod=c("none","doublet.scDblFinder"),
      filt=c("none","filt.default","filt.stringent"),
      norm=c("norm.seurat","norm.sctransform","norm.scran"),
      sel=c("sel.vst","sel.deviance","sel.expr"),
      selnb=c(2000,4000),
      dr=c("seurat.pca"),
      dims=c("elbow", 10, "maxLikGlobal"),
      clustmethod=c("clust.seurat","clust.scran.knnAnnoy") )
```

@@

# Supplementary Figure `r getFigNb(TRUE)`

@@

H1 <- renameHrows( scrna_evalPlot_silh(ov, agg.by = c("doubletmethod","filt","norm"), row_split = rnfn(norm),
                                       heatmap_legend_param=list(direction="horizontal"),font_factor = 0.8,
                                       row_names_max_width=unit(7, "cm")), rnfn)
H2 <- renameHrows(
     evalHeatmap(ov, step="clustering", what=c("MI","min_pr"), anno_legend=FALSE, title=c("MI","Min precision"), 
                 agg.by=c("doubletmethod","filt","norm"), font_factor = 0.8, 
                 row_split=rnfn(norm),row_names_max_width=unit(7, "cm")) + 
    evalHeatmap(ov, step="clustering", what=c("ARI"), agg.by=c("doubletmethod","filt","norm"), 
                row_split=rnfn(norm),filter=n_clus==true.nbClusts, title="ARI at true k",
                anno_legend=FALSE, font_factor = 0.8, row_names_max_width=unit(7, "cm")),
  rnfn)

@@

```{r, fig.width=9, fig.height=8.5}
plot_grid( grid.grabExpr(draw(H1, heatmap_legend_side="bottom")), 
           grid.grabExpr(draw(H2)), nrow=2, labels=LETTERS[1:2])
```

### Supplementary Figure `r getFigNb()`

@@

# Supplementary Figure `r getFigNb(TRUE)`

### Supplementary Figure `r getFigNb()`

>>>>

---
title: "Supplementary Figures relative to feature selection"
author: "Pierre-Luc Germain"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: pdf_document
---

@@

suppressPackageStartupMessages({
  library(ggplot2)
  library(ggrepel)
  library(cowplot)
  library(ComplexHeatmap)
  library(pipeComp)
})
theme_set(theme_cowplot(font_size = 11))
source("../misc_functions.R")
```

# Fig S`r getFigNb(TRUE)`

```{r, fig.align="center", echo=FALSE, out.height="0.95\\textheight"}
knitr::include_graphics("../main_figures/overall.pdf")
```

### Fig S`r getFigNb()`

**Overview of the combination of main alternative parameters.** Unsupervised clustering of the results (above) and top results (below). The color-mapping schemes are the same as described in the main figures.

@@

# Fig S`r getFigNb(TRUE)`

```{r, fig.width=6, fig.height=4}
ov <- readRDS("../data/overall.rds")
cl <- ov$evaluation$clustering
cl$norm <- relevel(cl$norm, "norm.seurat")
cl$doubletmethod <- relevel(cl$doubletmethod, "none")
cl$filt <- relevel(cl$filt, "none")
cl$sel <- relevel(cl$sel, "sel.vst")
cl$clustmethod <- relevel(cl$clustmethod, "clust.seurat")

# checking for interactions:
mod <- lm(ARI~resolution*dataset+doubletmethod*sel*filt*norm*clustmethod*dims, data=cl)
co <- as.data.frame(coef(summary(mod)))
coi <- co[grep(":",row.names(co)),]
coi <- coi[grep("dataset", row.names(coi), invert=TRUE),]
colnames(coi) <- c("Estimate","SE","t","p.value")
coi <- coi[order(coi$p.value),]
coi$FDR <- p.adjust(coi$p.value, method="fdr")
row.names(coi) <- gsub("selsel","sel",gsub("normnorm","norm",row.names(coi)))
coi$interaction <- gsub(":"," +\n", row.names(coi))
coi2 <- coi[coi$FDR < 0.05,]
ggplot(coi, aes(Estimate, -log10(p.value), label=interaction)) + geom_point() + 
  geom_point(data=coi2, colour="red") + geom_label_repel(data=coi2) + xlab("ARI coefficient") +
  ggtitle("Significant interactions between parameter values")
```

### Fig S`r getFigNb()`

Estimated coefficient and -log10 significance of all interaction coefficients in the linear model defined by

`ARI~dataset*resolution+doubletmethod*sel*filt*norm*clustmethod*dims`

Those terms significant at a FDR < 0.05 are highlighted. The top interaction terms are:

```{r}
knitr::kable(coi[1:10,c(1,2,4,5)], digits=3)
```

# Fig S`r getFigNb(TRUE)`

@@

@@

### Fig S`r getFigNb()`

@@

### 2020-08-04 supplementary_figures/supp_svadea.Rmd
updated supplementary figures, changing figure labels

### Supplementary Figure `r getFigNb()`
Accuracy of the differential expression analysis across combinations of: **A:** filters and DEA methods (using max 1 variable), **B:** filters and SVA methods (using max 1 variable), **C:** SVA methods (using 2 variables). In **C**, filled points indicate a nominal FDR below the observed FDR.

@@

### Supplementary Figure `r getFigNb()`
**A:** Accuracy of the estimated logFC (correlation and median absolute deviation from expected logFCs) and of the differential expression analysis (TPR stands for True Positive Rate, and FDR for False Discovery Rate) across the different combinations of SVA and DEA methods (using max 1 dimension). **B:** Running times of the different methods.

>>>>

### Fig S`r getFigNb()`
Accuracy of the differential expression analysis across combinations of: **A:** filters and DEA methods (using max 1 variable), **B:** filters and SVA methods (using max 1 variable), **C:** SVA methods (using 2 variables). In **C**, filled points indicate a nominal FDR below the observed FDR.

@@

### Fig S`r getFigNb()`
**A:** Accuracy of the estimated logFC (correlation and median absolute deviation from expected logFCs) and of the differential expression analysis (TPR stands for True Positive Rate, and FDR for False Discovery Rate) across the different combinations of SVA and DEA methods (using max 1 dimension). **B:** Running times of the different methods.
